Quarto Template for Springer Nature

### 2025-10-07 analysis/paper/access-ice.qmd
Uses Nature template

---
editor:
  markdown:
    wrap: sentence
title: Evaluation of +S2 sea ice forecast and some other better title
pdf-engine: pdflatex
journal:
  name: tc
author:
  - given_name: Elio 
    surname: Campitelli
    affiliation: "1,2"
    email: elio.campitelli@monash.edu
    corresponding: true
  - given_name: Ariaan 
    surname: Purich
    affiliation: "1,2"
  - given_name: Julie
    surname: Arblaster
    affiliation: "1,2"
  - given_name: Eun-Pa
    surname: Lim
    affiliation: "3"
  - given_name: Matthew
    surname: Wheeler
    affiliation: "3"
  - given_name: Phillip
    surname: Reid
    affiliation: "3"

affiliation:
  - code: 1
    address: School of Earth, Atmosphere and Environment, Monash University, Australia
  - code: 2
    address: Securing Antarctica’s Environmental Future, Monash University, Australia
  - code: 3
    address: Bureau of Meteorology

abstract: The abstract goes here.
bibliography: references.bib
running:
  title: +S2 sea ice forecast
  author: Campitelli et al.
# This section is mandatory even if you declare that no competing interests are present.
competinginterests: The authors declare no competing interests.
# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed. 
# Note: additional copyright statements for affiliated software or data need to be placed in the data availability section. 
copyrightstatement: The author's copyright for this publication is transferred to institution/company. 
### The following commands are for the statements about the availability of data sets and/or software code corresponding to the manuscript.
### It is strongly recommended to make use of these sections in case data sets and/or software code have been part of your research the article is based on.
### Note: unless stated otherwise, software and data affiliated with the manuscript are assumed to be published under the same licence as the article (currently Creative Commons 4.0)
availability:
  #code: |
  #  use this to add a statement when having only software code available
  #data: |
  #  use this to add a statement when having only data sets available
  codedata: use this to add a statement when having data sets and software code available
  sample: use this section when having geoscientific samples available
  videosupplement: use this section when having video supplements available
  authorcontribution: Contributions
  disclaimer: We like Copernicus.
  acknowledgements: Acknowledgements will gohere
  appendix: |
    \section{Figures and tables in appendices}
    Regarding figures and tables in appendices, the following two options are possible depending on your general handling of figures and tables in the manuscript environment:
    \subsection{Option 1}
    If you sorted all figures and tables into the sections of the text, please also sort the appendix figures and appendix tables into the respective appendix sections.
    They will be correctly named automatically.
    \subsection{Option 2}
    If you put all figures after the reference list, please insert appendix tables and figures after the normal tables and figures.

    To rename them correctly to A1, A2, etc., please add the following commands in front of them:
    `\appendixfigures` needs to be added in front of appendix figures
    `\appendixtables` needs to be added in front of appendix tables

    Please add `\clearpage` between each table and/or figure.

format: pdf

@@

filters:
  - ../../_extensions/pandoc-ext/abstract-section/abstract-section.lua
  # - ../../_extensions/mloubout/critic-markup/critic-markup.lua
  - ../../_extensions/ute/search-replace/search-replace.lua
search-replace:
  +S2: ACCESS-S2
  +S1: ACCESS-S1
  +CDR: NOAA/NSIDC CDRV4
---

>>>>

---
title: Quarto Template for Springer Nature
format:
  nature-pdf:
    # journal.cite-style is included in the tex file but ignored by pandoc if 
    # cite-method is not `natbib`.
    journal:
      cite-style: sn-nature
    # `citeproc` is the pandoc default. Set `cite-method: natbib` if required
    # to use the bst styles from the upstream template.
    cite-method: natbib
    keep-tex: true
    equal-margins: false
    classoption: referee
author:
  - name: Author One
    affiliations:
      - name: Harvard University
        id: 1
        department: Department of Government
        address: 1737 Cambridge Street
        city: Cambridge
        state: MA
        postal-code: 02138
      - name: Harvard University
        id: 2
        department: Department of Statistics
        address: 1 Oxford Street
        city: Cambridge
        state: MA
        postal-code: 02138
    attributes:
      equal-contributor: true
  - name: Author Two
    affiliations:
      - name: Yale University
        id: 3
        department: Department of Political Science
        address: 115 Prospect Street
        city: New Haven
        state: CT
        postal-code: 06511
    email: corresponding@email.com
    attributes:
      equal-contributor: true
      corresponding: true
  - name: Author Three
    affiliations:
      - ref: 1
abstract: |
  The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. Authors are advised to check the author instructions for the journal they are submitting to for word limits and if structural elements like subheadings, citations, or equations are permitted.
keywords: [template, demo]
bibliography: bibliography.bib

@@

filters:
  - ../../_extensions/pandoc-ext/abstract-section/abstract-section.lua
  # - ../../_extensions/mloubout/critic-markup/critic-markup.lua
  - ../../_extensions/ute/search-replace/search-replace.lua
search-replace:
  +S2: ACCESS-S2
  +S1: ACCESS-S1
  +CDR: NOAA/NSIDC CDRV4

---
